Time--Frequency Scattering Accurately Models Auditory Similarities Between Instrumental Playing Techniques

### 2020-10-26 paper/paper.tex
re-title subsections in related work section

\subsection*{Timbre modeling in music information retrieval (MIR)}
On the one hand, most publications in music information retrieval cast timbre modeling as an audio classification problem  \cite{martin1998asa,brown1999jasa,eronen2000icassp,herrera2003jnmr,wieczorkowska2003jiis,livshin2004dafx,krishna2004icassp,kaminskyj2005jiis,benetos2006icassp,bhalke2016jiis}.
In this context, the instrumentation of each musical excerpt serves as an unstructured set of ``audio tags,'' encoded as binary outputs within some predefined label space.
Because such tags often belong to the metadata of music releases, the process of curating a training set for musical instrument classification requires little or no human intervention.
Although scraping user-generated content from online music platforms may not always reflect the true instrumentation with perfect accuracy, it offers a scalable and ecologically valid insight onto the acoustic underpinnings of musical timbre.

@@

\subsection*{Timbre modeling in music cognition research}
On the other hand, the field of music psychology investigates timbre with the aim of discovering its physiological and behavioral foundations \cite{mcadams2009chapter}.
In this setting, prior knowledge of instrumentation, however accurate, does not suffice to conduct a study on timbre perception.
Rather, each excerpt must be played back to multiple human listeners.
Yet, collecting subjective responses to acoustic stimuli is a tedious and unscalable procedure, which restricts the size of the musical corpus under study.
These small corpus sizes hampers the applicability of optimization algorithms for representation learning, such as stochastic gradient descent in deep neural networks.

>>>>

\subsection*{Automatic classification of musical instruments and playing techniques}
On the one hand, most publications in music information retrieval cast timbre modeling as an audio classification problem  \cite{martin1998asa,brown1999jasa,eronen2000icassp,herrera2003jnmr,wieczorkowska2003jiis,livshin2004dafx,krishna2004icassp,kaminskyj2005jiis,benetos2006icassp,bhalke2016jiis}.
In this context, the instrumentation of each musical excerpt serves as an unstructured set of ``audio tags,'' encoded as binary outputs within some predefined label space.
Because such tags often belong to the metadata of music releases, the process of curating a training set for musical instrument classification requires little or no human intervention.
Although scraping user-generated content from online music platforms may not always reflect the true instrumentation with perfect accuracy, it offers a scalable and ecologically valid insight onto the acoustic underpinnings of musical timbre.

@@

\subsection*{Spectrotemporal receptive fields (STRF) in music cognition}
On the other hand, the field of music psychology investigates timbre with the aim of discovering its physiological and behavioral foundations \cite{mcadams2009chapter}.
In this setting, prior knowledge of instrumentation, however accurate, does not suffice to conduct a study on timbre perception.
Rather, each excerpt must be played back to multiple human listeners.
Yet, collecting subjective responses to acoustic stimuli is a tedious and unscalable procedure, which restricts the size of the musical corpus under study.
These small corpus sizes hampers the applicability of optimization algorithms for representation learning, such as stochastic gradient descent in deep neural networks.
